Verification of Stencil Computations through Spatial Specifications

### 2016-07-06 paper.tex
eliminate an overflow
slight adjustment to tab:corpus

Note that if the specification was as follows:
%
\begin{minted}{fortran}
!= stencil atLeast, readOnce, fivepoint :: b}
\end{minted}
%
The consistency function would have held as
$\mathit{cons}(\textsf{mult}(\textsf{up}(m)),L3',b)$ for the upper bound would
have never been needed. This semantically makes sense since the region
$\texttt{fivepoint}$ is indeed a lower bound for the access pattern of $b$.

@@

\subsection{Software Corpus}
\begin{table}
\centering
\footnotesize
\begin{tabular}{lSSSS}
\hline
& \multicolumn{2}{c}{Number of files} & \multicolumn{2}{c}{Lines of code} \\

>>>>

Note that if the specification was as follows:
%
\begin{minted}{fortran}
!= stencil atLeast, readOnce, fivepoint :: b}
\end{minted}
%
The consistency function would have held because for the upper bound
$\mathit{cons}(\textsf{mult}(\textsf{up}(m)),L3',b)$ would never have
been needed. This semantically makes sense since the region
$\texttt{fivepoint}$ is indeed a lower bound for the access pattern of
$b$.

@@

\subsection{Software Corpus}
\begin{table}
\centering
\footnotesize
\begin{tabular}{lS[table-format=4]S[table-format=4]SS}
\hline
& \multicolumn{2}{c}{Number of files} & \multicolumn{2}{c}{Lines of code} \\
